\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-02-19 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
keep on updating

\noindent The ${\underline {\underline \sigma}}_{\alpha}=\mu_\alpha S_\alpha \left(\mathcal{K}_{{r}_\alpha}\mathbf{K}\right)^{-1}$ represents the implicit linearisation of the viscous frictional forces. Assuming a porous media domain $\Omega\subset\mathcal{R}^{n}$ ($n$ is the number of dimensions). 
\end{comment}
%%%%%%%%%%%%%%%
\begin{comment}
The displacing and displaced fluids are considered to be incompressible and immiscible under isothermal and no source or sink conditions. In addition, we neglect the effects of capillarity and gravity in our simulations. Therefore the governing equations of conservation of mass and Darcy's law can be described below as,

@@

 Defining the advective velocity averaged over the entire domain -- $\mathbf{u}_{\alpha}= \mathbf{q}_{\alpha}/S_{\alpha}$, then we may rewrite Eq.(\ref{E:darcy_ext}),
\begin{equation}
  {\underline {\underline \sigma}}_{\alpha} \mathbf{u}_{\alpha} = - \nabla p + {\mathbf{s}_{u}}_{\alpha},
  \label{E:darcy_ext}
\end{equation}
$\underline{\underline{\sigma}}_{\alpha}=\mu_{\alpha}S_{\alpha}\left(\mathcal{K}_{r\alpha}\mathbf{K}\right)^{-1}$ represents the implicit linearisation of the viscous frictional forces, and is piecewise constant within each FE and is obtained via basis functions local to each CV within each element \citep{Jackson13,Radunz14}.
\end{comment}

@@

As we have to be consistent with \citet{jackson_2015} we assume that rick and fluids are incopressible thus the mass ballance for phase $\alpha$ can be written as (Eq.\ref{mass_balance})

\begin{equation}
\phi \; \frac{\partial S_{\alpha}}{\partial t} + \nabla (v_{\alpha}S_{\alpha})= q_{\alpha}
\label{mass_balance}
\end{equation}

where $\phi$ represents the porosity, S represents the saturation and v is the saturation weighted Darcy velocity (such that $v_{\alpha}S_{\alpha}$ is the traditional Darcy velocity of phase p), and q is a volume source term, subject to the contrains on the saturation

\begin{equation}
\sum  S_{p}-1
\label{saturation_constrain}
\end{equation}

The Eq.\ref{saturation_constrain}, is discretized in time and space following the approach of \citet{Jackson_2013} in which the time discretization is obtained using the $\theta$-method as implemented by %\citet{gomes_2013}. 
Summing over all phases and discretizing in time using the $\theta$-method yields the global mass balance equation, Eq.\ref{global_mass_balance},

>>>>

\noindent The ${\underline {\underline \sigma}}_{\alpha}=\mu_\alpha S_\alpha \left(\mathcal{K}_{{r}_\alpha}\mathbf{K}\right)^{-1}$ represents the implicit linearisation of the viscous frictional forces. Assuming a porous media domain $\Omega\subset\mathcal{R}^{n}$ ($n$ is the number of dimensions). 
\end{comment}

%%%%%%%%%%%%%%%
\begin{comment}
The displacing and displaced fluids are considered to be incompressible and immiscible under isothermal and no source or sink conditions. In addition, we neglect the effects of capillarity and gravity in our simulations. Therefore the governing equations of conservation of mass and Darcy's law can be described below as,

@@

 Defining the advective velocity averaged over the entire domain -- $\mathbf{u}_{\alpha}= \mathbf{q}_{\alpha}/S_{\alpha}$, then we may rewrite Eq.(\ref{E:darcy_ext}),
\begin{equation}
  {\underline {\underline \sigma}}_{\alpha} \mathbf{u}_{\alpha} = - \nabla p + {\mathbf{s}_{u}}_{\alpha},
  \label{E:darcy_ext}
\end{equation}
$\underline{\underline{\sigma}}_{\alpha}=\mu_{\alpha}S_{\alpha}\left(\mathcal{K}_{r\alpha}\mathbf{K}\right)^{-1}$ represents the implicit linearisation of the viscous frictional forces, and is piecewise constant within each FE and is obtained via basis functions local to each CV within each element \citep{Jackson13,Radunz14}.
\end{comment}
%%%%%%%%%%%%%%%

@@

In this model we assume that rock and fluids are incopressible thus the mass ballance for phase $\alpha$ can be written as (Eq.\ref{mass_balance})

\begin{equation}
\phi \; \frac{\partial S_{\alpha}}{\partial t} + \nabla (u_{\alpha}S_{\alpha})= \mathcal{S}_{cty,\alpha}
\label{mass_balance}
\end{equation}

%\noindent where $\phi$ represents the porosity, S represents the saturation and v is the saturation weighted Darcy velocity (such that $v_{\alpha}S_{\alpha}$ is the traditional Darcy velocity of phase p), and q is a volume source term, subject to the contrains on the saturation

%\begin{equation}
%\sum  S_{p}-1
%\label{saturation_constrain}
%\end{equation}

Equation \ref{mass_balance}, is discretize in time and space following the $\theta$-method. Summing over all phases and discretizing in time using the $\theta$-method yields the global mass balance equation %\ref{global_mass_balance},

\medskip
The discretised global mass and force balance equations are solved using a multigrid-like approach ,see \citet{pavlidis2016}.
